Supplementary Material

### 2021-10-22 analysis/paper/paper.Rmd
add table to supplementary materials

```{r sample-count}
samp_counts <- corr_comb_long %>%
  pivot_wider(names_from = size, values_from = count) %>%
  ungroup() %>%
  add_row(select(samp_comb_row, !sample), .after = 2)

samp_sd_wide <- corr_sd_long %>%
  select(!count) %>%
  pivot_wider(names_from = size, values_from = sd) %>%
  ungroup() %>%
  add_row(samp_sd_row, .after = 2) %>%
  mutate(across(where(is.numeric), round)) %>%
  rename(s_sd = s,
         m_sd = m,
         l_sd = l,
         total_sd = total)

samp_counts_per <- samp_counts %>%
  mutate(across(c(s, m, l, total), 
                function(x) 
                  paste0(round(x), " (", scales::percent(signif(x / total, 3)), 
                         ")")))

>>>>

```{r sample-count}
samp_counts_per <- samp_counts %>%
  mutate(across(c(s, m, l, total), 
                function(x) 
                  paste0(round(x), " (", scales::percent(signif(x / total, 3)), 
                         ")")))

### 2021-10-22 analysis/supplementary-materials/supp-mat.Rmd
add table to supplementary materials

```{r setup, include=FALSE}
library(here)
library(tidyverse)
library(patchwork)
source(here("analysis/scripts/analysis.R"))
source(here("analysis/scripts/figures.R"))
#raw_data_samples <- read_csv(here("analysis/data/raw_data/starch_counts.csv"))
#raw_data_solutions <- read_csv(here("analysis/data/raw_data/solution_counts.csv"))
```

@@

```{r amylase-activity-results, message=FALSE}
# table of results reported in units amylase per mL enzyme (but let's be honest,
  # ...it doesn't really matter what the unit is. No activity is no activity)
source(here("analysis/scripts/amylase-assay.R"))
cols <- c("1", "2", "3")  # sample triplicates
rows <- c("S1", "S2", "S3", "B1", "B2", "B3", "B4", "B5", "BT1", "BT2", "BT3")
plt1_ph1_result <- rbind(sal1_ph1, bmm1_ph1)
rownames(plt1_ph1_result) <- rows
plt1_ph2_result <- rbind(sal1_ph2, bmm1_ph2)
rownames(plt1_ph2_result) <- rows
plt2_ph1_result <- rbind(sal2_ph1, bmm2_ph1)
rownames(plt2_ph1_result) <- rows
plt2_ph2_result <- rbind(sal2_ph2, bmm2_ph2)
rownames(plt2_ph2_result) <- rows
```

@@

>>>>

```{r setup, include=FALSE}
library(here)
library(tidyverse)
library(patchwork)
source(here("analysis/scripts/analysis.R"))
source(here("analysis/scripts/figures.R"))
source(here("analysis/scripts/tables.R"))
source(here("analysis/scripts/amylase-assay.R"))
#raw_data_samples <- read_csv(here("analysis/data/raw_data/starch_counts.csv"))
#raw_data_solutions <- read_csv(here("analysis/data/raw_data/solution_counts.csv"))
```

@@

```{r amylase-activity-results, message=FALSE}
# table of results reported in units amylase per mL enzyme (but let's be honest,
  # ...it doesn't really matter what the unit is. No activity is no activity)
cols <- c("1", "2", "3")  # sample triplicates
rows <- c("S1", "S2", "S3", "B1", "B2", "B3", "B4", "B5", "BT1", "BT2", "BT3")
plt1_ph1_result <- rbind(sal1_ph1, bmm1_ph1)
rownames(plt1_ph1_result) <- rows
plt1_ph2_result <- rbind(sal1_ph2, bmm1_ph2)
rownames(plt1_ph2_result) <- rows
plt2_ph1_result <- rbind(sal2_ph1, bmm2_ph1)
rownames(plt2_ph1_result) <- rows
plt2_ph2_result <- rbind(sal2_ph2, bmm2_ph2)
rownames(plt2_ph2_result) <- rows
```

@@

### ...and a table

Differences in size ratios (%) of granules between the solutions and the samples. 
Negative values indicate a loss of granules from solution to sample.

```{r diff-tbl}
size_diff %>%
  mutate(across(where(is.numeric), signif, 3))
```
